Biodiversity of Japanese Pteridophytes

### 2019-06-28 reports/japan_pteridos_biodiv.Rmd
Simplify extraction of r2 with glance()

# Two ways to fit the model:
# GLM
glm_sum <- glm(pd_obs + 0.0001 ~ richness, data=alpha_div_pteridos, family=Gamma(link="log")) %>%
  summary

# Linear model after log transform. This one gives us an R-squared.
lm_sum <- lm(-log(pd_obs + 0.0001) ~ richness, data = alpha_div_pteridos) %>% summary

# Extract R-squared.
pd_by_rich_r2 <- lm_sum[['adj.r.squared']] %>% round(2)

```{r ses_pd-by-rich-summary}
# Run linear model of ses PD vs. richness across all pteridophytes and
# extract R2 and pvalue for mentioning in text.

# Linear model after log transform. This one gives us an R-squared.
ses_pd_rich_sum <- lm(ses_pd ~ richness, data = alpha_div_pteridos) %>% summary

# Extract R-squared.
ses_pd_by_rich_r2 <- ses_pd_rich_sum[['adj.r.squared']] %>% round(2)

# P is very very small
tidy(ses_pd_rich_sum)

```
### Phylogenetic diversity (PD) calculations

@@

```{r pd-by-el-summary}
# Run linear model of SES of PD vs. elevation in northern ferns dataset
pd_by_el_summary <- lm(ses_pd ~ elevation, alpha_div_ferns_north_south) %>% summary

# Extract R2 and pvalue for mentioning in text.
pd_by_el_r2 <- pd_by_el_summary[['adj.r.squared']] %>% round(2)

# P is very very small
pd_by_el_summary %>% tidy %>% filter(term == "elevation") %>% pull(p.value)

@@

>>>>

# Two ways to fit the model:
# GLM
pd_by_rich_glm_mod <- glm(pd_obs + 0.0001 ~ richness, data=alpha_div_pteridos, family=Gamma(link="log"))
summary(pd_by_rich_glm_mod)

# Linear model after log transform. This one gives us an R-squared.
pd_by_rich_lm_mod <- lm(-log(pd_obs + 0.0001) ~ richness, data = alpha_div_pteridos)

# Extract R-squared.
pd_by_rich_r2 <- pd_by_rich_lm_mod %>% glance %>% pull(r.squared) %>% round(3)

# P is very very small, effectively 0
pd_by_rich_lm_mod %>% glance
```

```{r ses_pd-by-rich-summary}
# Run linear model of ses PD vs. richness across all pteridophytes and
# extract R2 and pvalue for mentioning in text.
ses_pd_rich_mod <- lm(ses_pd ~ richness, data = alpha_div_pteridos)

# Extract R-squared.
ses_pd_by_rich_r2 <- ses_pd_rich_mod %>% glance %>% pull(r.squared) %>% round(3)

# P is very very small
ses_pd_rich_mod %>% glance
```

### Phylogenetic diversity (PD) calculations

@@

```{r pd-by-el-summary}
# Run linear model of SES of PD vs. elevation in northern ferns dataset
pd_by_el_mod<- lm(ses_pd ~ elevation, alpha_div_ferns_north_south)

# Extract R2 and pvalue for mentioning in text.
pd_by_el_r2 <- pd_by_el_mod %>% glance %>% pull(r.squared) %>% round(3)

# P is very very small
pd_by_el_mod %>% glance
```

@@

### Breeding system

```{r ses-pd-vs-perc-sex-dip-summary}
# Run linear model of SES of PD vs. percentage of sexual diploid ferns
ses_pd_vs_repro_ferns_mod <- lm(ses_pd ~ percent_sex_dip, ses_pd_vs_repro_ferns)

# Extract R2 and pvalue for mentioning in text.
ses_pd_vs_repro_ferns_r2 <- ses_pd_vs_repro_ferns_mod %>% glance %>% pull(r.squared) %>% round(3)

# P is very very small
ses_pd_vs_repro_ferns_mod %>% glance
```

Sexual diploid taxa tend to be distributed in northern latitudes (Fig. \@ref(fig:sex-dip-ferns-map)).

Somewhat surprisingly, SES of PD shows a negative relationship with the percentage of sexual diploid taxa (Fig. \@ref(fig:ses-pd-vs-perc-sex-dip); *R*^2^ = `r ses_pd_vs_repro_ferns_r2`, *P* << 0.05). We expected that since many apogamous (non-sexual) taxa have identical or very similar DNA sequences to their sexual relatives that communities with more apogamous taxa would be more clustered and communities with more sexual diploids would be overdispersed. It seems that communities with many non-sexual taxa actually tend to include distantly related taxa rather than sister pairs of sexual and non-sexual species.
